Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-14 paper/ijcai/paper.tex
more fixes

\subsection{Combining \sfl{} and \cs{}}
\label{sec:comb}

To illustrate the idea behind the combination of \sfl{} with \cs{}, consider a
debugging scenario with five components $c_{1..5}$ and five
transactions $t_{1..5}$, two of which are failing. Consider,
additionally, that the component $c_2$ is faulty.
Figure~\ref{fig:illustration} shows, at the left-hand side of the
arrow ($\Rightarrow$), an hypothetical spectra and its corresponding
ranking, produced with the Ochiai predictor. Each line in the ranking
shows, respectively, the rank/position, the component label, and the
Ochiai score (in parentheses).

@@

@@

\begin{figure}[h]
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Nemenyi post-hoc analysis results \Sof{Considering \chart{}, \jtime{}, \mockito{}, \lang{} }}
		\label{fig:performance}
\end{figure}

>>>>

\subsection{Combining \sfl{} and \cs{}}
\label{sec:comb}
\Sof{@todo: define slicer - set of statements}
To illustrate the idea behind the combination of \sfl{} with \cs{}, consider a
debugging scenario with five components $c_{1..5}$ and five
transactions $t_{1..5}$, two of which are failing. Consider,
additionally, that the component $c_2$ is faulty.
Figure~\ref{fig:illustration} shows, at the left-hand side of the
arrow ($\Rightarrow$), an hypothetical spectra and its corresponding
ranking, produced with the Ochiai predictor. Each line in the ranking
shows, respectively, the rank/position, the component label, and the
Ochiai score (in parentheses).

@@

The oracle idea is based on the statement deletion mutant operator. This operator was designed based on 
the idea that each statement has an effect on the test output (i.e., oracle).

@@

\begin{figure}[h]
		\includegraphics[width=0.45\textwidth]{figures/heatmap_nemenyi_result.pdf}
		\caption{Nemenyi post-hoc analysis results \Sof{@tofix: Need to center ylabels}}
		\label{fig:performance}
\end{figure}
